\section{Introduction}

Cellular networks are operated through structured telemetry rather than a single homogeneous signal. A cell-level operations panel may contain continuous KPI and business counters, sparse alarm/fault events, cell identifiers, and time context. KPI histories describe load, accessibility, retainability, throughput and radio-quality dynamics; alarms mark discrete operational events; cell and time features encode persistent local behavior and periodic demand. Anticipatory mobile networking and traffic-prediction studies have shown that prediction can support proactive resource management and operational optimization \cite{bui2017anticipatory,zhang2019deepmobile}. For cellular operations, anticipating KPI degradation is useful because it can surface risky cell states before manual inspection or customer impact.

The modeling difficulty is that these signals are heterogeneous. Pure KPI-history models can exploit strong temporal regularities, but they may ignore sparse event context that operators naturally inspect during fault handling. Pure alarm/event models, on the other hand, are often insufficient for continuous KPI prediction because alarm occurrences are rare and many KPI changes follow routine traffic or radio patterns rather than explicit faults. Prior cellular traffic work has emphasized spatial and temporal dependencies among base stations \cite{wang2017spatiotemporal,sun2022mobiletraffic}, while alarm-correlation work has long noted that a single fault may generate many related alarms and that fault isolation is difficult in large communication networks \cite{jakobson1993alarm,bouloutas1994alarm}. In enterprise operations data, the problem is harder still: physical topology may be unavailable, expert root-cause annotations may be absent, and data release may be restricted by business and network-operation confidentiality.

This paper studies a cautious technical pipeline for this setting. We propose CET-STGL, a causal-inspired event-token spatio-temporal learning framework for alarm-driven KPI degradation prediction. The framework represents KPI histories as patch features, sparse alarms as event tokens and decayed intensities, cell/time information as positional features, and train-only alarm-degradation associations as an event influence prior. A cross-cell graph is inferred from available training statistics when physical topology is not present. The term causal-inspired is used deliberately: the graph organizes temporal association and event-influence hypotheses, but the observational data do not support confirmed causal discovery.

The study is deliberately narrower than telecom foundation-model or benchmark work. Recent telecom LLM studies and datasets target language or standards knowledge \cite{maatouk2025llmtelecom,maatouk2026teleqna,zou2025telecomgpt}; our problem is instead structured telemetry learning over a private enterprise operations panel. We do not train a telecom foundation model, do not release a public benchmark, do not claim strict causality, do not claim expert-confirmed root-cause validation, and do not report unrun neural baselines. Forecasting labels are real future KPI values. Degradation labels and root-cause ranking labels are weak labels derived from training-split KPI thresholds and train-only alarm-lift rules, following the broader weak-supervision view that noisy or indirect labels can be useful but should not be equated with ground truth \cite{zhou2018weakly,ratner2020snorkel}.

Our contributions are:
\begin{enumerate}
    \item We formulate alarm-driven KPI degradation prediction as a multi-task learning problem over real cellular KPI/business and alarm/fault panels.
    \item We design a causal-inspired event-token representation that combines KPI patch tokens, alarm event tokens, cell/time positional features, train-only event influence priors and inferred cross-cell graph context.
    \item We provide a leakage-controlled experimental protocol for 1/3/6/12-hour KPI forecasting, weak degradation classification and weak root-cause candidate ranking.
    \item We report calibrated findings: KPI-history baselines remain strong, event-only and Hawkes-only variants are weak standalone predictors, the runnable CET-STGL sklearn proxy is competitive on several primary-KPI forecasting metrics, and alarm-token gains are not uniform under current weak labels.
\end{enumerate}
