\section{Discussion and Limitations}

The experiments support a technical but bounded conclusion. CET-STGL is useful as a representation framework for combining KPI history, sparse alarms, cell/time context and inferred graph information. The runnable sklearn proxy is competitive with Ridge/Logistic on several primary-KPI forecasting metrics, and the ablations show which representation blocks are active in the current data. At the same time, the results do not support broad claims of alarm-token superiority or broad neural-graph superiority.

The main empirical lesson is that KPI history is strong. This is expected for hourly KPI and business panels with regular load and radio patterns. Alarm features are operationally meaningful, but they are sparse in this slice. Therefore, event-only and Hawkes-only variants are weak standalone predictors. Their weakness strengthens the methodological point: alarms should be integrated with KPI context and treated as event-conditioned evidence, not used alone to explain KPI degradation.

The root-cause ranking task is intentionally framed as weak-label consistency. High Hit@K or MRR values indicate agreement with train-only proxy labels, not expert-confirmed root-cause localization. This is especially important because some ranking scores use signals related to the weak-label construction. Expert incident tickets, work orders or validated root-cause annotations would be required for true operational RCA evaluation.

Several limitations remain. First, the data are private and come from one project slice, so the work is not a public benchmark and does not establish broad generalization across operators or regions. Second, degradation and ranking labels are weak labels; only forecasting uses real future KPI targets. Third, the event influence graph is causal-inspired rather than strictly causal. Observational associations cannot establish causality without interventions, counterfactual assumptions or external validation. Fourth, neural baselines were not run because PyTorch is unavailable; LSTM, TCN, Informer, Autoformer, STGCN and GAT remain future implementation targets. Fifth, the cross-cell graph is inferred statistically rather than verified from physical topology.
